The non-random assembly of indirect interactions in  \nplant-pollinator networks

### 2022-07-20 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
edits

Ecological communities are formed by a plethora of interacting species that form networks of interactions. Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020]. Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale). For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007]. In addition, the local species position within the network can define its degree of specialisation [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007]. Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].

>>>>

Ecological communities are formed by a plethora of interacting species that form networks of interactions. Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020]. Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale). For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007]. In addition, the local species position within the network can define its degree of specialisation [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007]. Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
